worldmap

### 2022-09-19 analysis/figures/visualization.Rmd
Update figures to exclude amphibians

```{r}
pins::board_register_github(repo = "karinorman/biodivTS_data", branch = "master")
# country_data <- pins::pin_get("country-data-bind", board = "github") %>%
#   mutate(country = str_remove(country, "Commonwealth of The "),
#          country = str_remove(country, "Kingdom of "),
#          country = str_remove(country, "Republic of "),
#          country = str_remove(country, "Kingdom of "),
#          country = str_remove(country, "Federative Republic of "),
#          country = str_remove(country, "Federative "),) %>%
#   mutate(country = case_when(
#     country == "United States" ~ "USA",
#     country == "Russian Federation" ~ "Russia",
#     country == "United Great Britain and Northern Ireland" ~ "UK",
#     country == "Czechia" ~ "Czech Republic",
#     TRUE ~ country
#   )) %>% 
#   count(country, code)
# 
# mapdata <- map_data("world") %>%
#   left_join(country_data, by = c("region" = "country"))
# 
# mapdata %>%
#   ggplot(aes(long, lat)) +
#   geom_polygon(mapping = aes(group = group, fill = n)) +
#   ggthemes::theme_map() +
#   #scale_fill_continuous(color = "#32A251")
#   scale_fill_gradient(low = "white", high = "#39737c")

#ggsave("study_map.jpeg")
```

@@

#get rarefyid centers
included_ids <- pins::pin_get("model-data", board = "github") %>%
  select(rarefyID, taxa, climate, realm, duration) %>%
  distinct() %>% 
  mutate(rarefyID = str_replace_all(rarefyID, pattern = "_bird", ""), 
  rarefyID = str_replace_all(rarefyID, pattern = "_mamm", ""))

>>>>

```{r}
load(here::here("data/model_data.rda"))
```

@@

#get rarefyid centers
included_ids <- model_data %>%
  select(rarefyID, taxa, climate, realm, duration) %>%
  distinct() %>% 
  mutate(rarefyID = str_replace_all(rarefyID, pattern = "_bird", ""), 
  rarefyID = str_replace_all(rarefyID, pattern = "_mamm", ""))
